Identifying the L1 of non-native writers: the CMU-Haifa system\\[1em] {\large Chris Dyer$^\ast$ Manaal Faruqui$^\ast$ Noam Ordan$^\dagger$ Nathan Schneider$^\ast$\\ Yulia Tsvetkov$^\ast$ Naama Twitto$^\dagger$ Shuly Wintner$^\dagger$}\\[-3em]

### 2013-04-07 paper/paper.tex
brown, creg

@@

\begin{compactdesc}
\item[\feat{POS}] Part-of-speech $n$-grams.  Features were extracted
  to count every POS 1-, 2-, and 3-gram in each
  document. 53.92\%. \sw{But the table says 55.18}
\item[\feat{FreqChar}] Frequent character $n$-grams.  We experimented
  with character $n$-grams: The number of character 1-, 2-, and
  3-grams. This yielded 69.94\% accuracy.  We then refined the feature
  to include only those character $n$-grams that are observed more
  than $m$ times in the corpus are considered. \sw{$n$ ranges from~1
    to~4, and $m$ is set to~???. 74.12\%}
\item[\feat{CharPrompt}] Conjunction of the character $n$-gram
  features defined above with the prompt ID. 65.09\%.
\item[\feat{Brown}] Brown clusters. \sw{???}
\end{compactdesc}
\noindent
The accuracy of the classifier on the development set using these four
feature types is reported in \Tref{tbl:mainfeats}.

@@

\section{Results}
\label{sec:results}
The full model that we used to classify the test set combines all
features listed in \Tref{tbl:addfeats}. Using all these features, the
accuracy on the development set is \sw{???}, and on the test set it
is~81.5\%. \Tref{tbl:matrix} lists the confusion matrix on the test
set, as well as precision, recall and $F_1$-score for each L1.
The largest class of errors was predicting Telugu where the correct label 
was Hindi\nss{or vice versa?}---this happened 18 times.

>>>>

For classification we use the {\tt creg} regression modeling framework to train a 11-class logistic regression classifier.\footnote{https://github.com/redpony/creg}  We parameterize the L1 classifier as a multiclass logistic regression:
\begin{align*}
p(y& \mid \textbf{w}, i) \propto \exp \sum_j \lambda_j h_j(y, \textbf{w}, i) ,
\end{align*}
where $h_j(\cdot)$ are feature functions, $\lambda_j$ are the corresponding weights, and $y$ refer to the outputs: eleven L1 class labels. \yt{regularization???}

@@

\begin{compactdesc}
\item[\feat{POS}] Part-of-speech $n$-grams.  Features were extracted
  to count every POS 1-, 2-, 3- and 4-gram in each
  document. 55.18\%. 
\item[\feat{FreqChar}] Frequent character $n$-grams.  We experimented
  with character $n$-grams: The number of character 1-, 2-, and
  3-grams. This yielded 69.94\% accuracy.  We then refined the feature
  to include only those character $n$-grams that are observed more
  than $m$ times in the corpus are considered. \sw{$n$ ranges from~1
    to~4, and $m$ is set to~???. 74.12\%}
\item[\feat{CharPrompt}] Conjunction of the character $n$-gram
  features defined above with the prompt ID. 65.09\%.
\item[\feat{Brown}] Substitutions, deletions and insertions counts of Brown clusters 1- and 2-grams in each document. 72.26\%.
\end{compactdesc}
\noindent
The accuracy of the classifier on the development set using these four
feature types is reported in \Tref{tbl:mainfeats}.

@@

\section{Results}
\label{sec:results}
The full model that we used to classify the test set combines all
features listed in \Tref{tbl:addfeats}. Using all these features, the
accuracy on the development set is~84.55\%, and on the test set it
is~81.5\%. \Tref{tbl:matrix} lists the confusion matrix on the test
set, as well as precision, recall and $F_1$-score for each L1.
The largest class of errors was predicting Telugu where the correct label 
was Hindi\nss{or vice versa?}---this happened 18 times.
